companion files

### 2021-09-21 response-letter/response-letter.Rmd

Regards,

Nicholas Tierney & Karthik Ram

\newpage

\renewcommand{\arraystretch}{2}
```{r show-table}
our_table %>% 
  kbl(booktabs = TRUE,
      longtable = TRUE,
        linesep = "\\addlinespace") %>% 
  kable_styling(latex_options = c("striped",
                                  "hold_position", 
                                  "repeat_header"),
                full_width = TRUE) %>% 
  column_spec(1) %>% 
  column_spec(2, width = "20em") %>% 
  column_spec(3, width = "20em")
```

### 2021-09-22 companion-files.Rmd
make into word doc, remove extra details on what the blurbs are

---
title: "companion files"
output: html_document
---

@@

> The eTOC blurb is a short summary that describes the context and significance of the findings for the broader readership. Please see the "In Brief" links in the table of contents for examples. The blurb should be 80 words or fewer.

@@

> https://www.cell.com/patterns/authors

>>>>

---
title: "companion files"
output:
  word_document: default
  html_document: default
---

@@

@@
